### 2018-07-23 express2018/equa.tex
Fixed p.4, Def. 3.3: #32

\begin{definition}
A system of equations 
$\{  X_i = E_i\}_{i\in I}$
 is 
\begin{itemize}
\item
\emph{(strongly) guarded} if,  in each    $E_i$, each occurrence of
an \behav\  variable is underneath a visible prefix;

\item 
 \emph{sequential} if,  in each    $E_i$, each occurrence of
an \behav\  variable only appears  underneath prefixes and sums.
\end{itemize}
 \end{definition}

>>>>

\begin{definition}[guardedness of equations]
\label{def:guardness}
A system of equations 
$\{  X_i = E_i\}_{i\in I}$
 is 
\begin{itemize}
\item
\textbf{weakly guarded} if,  in each    $E_i$, each occurrence of
an \behav\  variable is underneath a prefix;

\item
\textbf{(strongly) guarded} if,  in each    $E_i$, each occurrence of
an \behav\  variable is underneath a \textbf{visible} prefix;

\item 
 \textbf{sequential} if,  in each    $E_i$, each of its subexpressions with occurrence of
an \behav\  variable, apart from the variable itself, is in forms of
prefixes or sums.
\end{itemize}
 \end{definition}
